\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage[UTF8]{ctex}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-16pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-8pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItemSingle}[1]{
\vspace{-4pt}
\linespread{1.2}
\item\small{
{#1 \vspace{-2pt}}
}}

\newcommand{\resumeItem}[2]{
\item\small{
\textbf{#1}{: #2 \vspace{-4pt}}
}}

\newcommand{\resumeSubheadingMininal}[1]{
\vspace{-0pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1}
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubheadingCompact}[2]{
\vspace{2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textit{\small #2}
    \end{tabular*}\vspace{-1pt}
    \vspace{-5pt}
}

\newcommand{\resumeSubheadingCompactVertical}[2]{
\vspace{-0pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1}
    \end{tabular*}\vspace{-0pt}
    #2
    \vspace{-6pt}
}

\newcommand{\resumeSubheadingExtended}[3]{
\vspace{-0pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2
    \end{tabular*}\vspace{-0pt}
    #3
    \vspace{-6pt}
}

\newcommand{\resumeSubheadingWithTime}[3]{
\vspace{-0pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-0pt}
    #3
    \vspace{-6pt}
}

\newcommand{\resumeSubheading}[4]{
\linespread{1.1}
\vspace{2pt}\item
\renewcommand{\arraystretch}{0.7}
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubItem}[2]{
\vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textit{\samll #2}
    \end{tabular*}\vspace{-14pt}
    }

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]\vspace{-1pt}}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-1pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-11pt}}


%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{\Large JUNFENG YU} \\
    \centerline{
        \footnotesize \textbf{Portf:} \href{https://jacob953.com/}{https://jacob953.com/} |
        \textbf{Email:} \href{mailto:i@jacob953.com}{i@jacob953.com} | 
        \textbf{LinkedIn:} \href{https://www.linkedin.cn/incareer/in/junfeng-yu-578456248}{https://www.linkedin.com/in/jacob953/} |
        \textbf{Mobile:} +86 155 8521 0953
    }
\end{tabular*}


%-----------Education Background-----------------
\section{Education Background}
\resumeSubHeadingListStart
    
    \resumeSubheading
    {Central South University (CSU)}{Changsha, China}
    {Bachelor of Engineering in Security Information}{Sept 2019 - June 2023}
        \resumeItemListStart
        \resumeItem{Courses}
        {Linear Algebra, Probability And Statistics, Computer Network,  Operating System, Database Principle and so on.}
        \resumeItem{Honor}
        {Outstanding Collegiate Dissertation. (---------------------------------------------------------------------------------)}
        \resumeItemListEnd
        
        
\resumeSubHeadingListEnd


%-----------Professional Experience-----------------
\section{Professional Experience}
\resumeSubHeadingListStart

    \resumeSubheading
    {Alibaba (Ant Group) - Alipay Business Line}{Hangzhou}
    {Java R\&D Engineer Intern at Alipay}
    {Nov 2022 - Present}
        \resumeItemListStart
        \resumeItem{Programmed}
        {---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------}
        \resumeItem{Influenced}
        {---------------------------------------------------------------------------------}
        \resumeItemListEnd
      
      
    \resumeSubheading
    {Huawei - 2012 Laboratories}{Xi'an}
    {Software Engineer Intern at GaussDB Laboratory}
    {July 2022 - Nov 2022}
        \resumeItemListStart
        \resumeItem{Chaired}
        {Pre-researched the development of database kernel trimming to solve the problem of insufficient memory in special scenarios by conserving database running memory footprint to 10\% of the original.}
        \resumeItem{Presentation}
        {The only Gauss SWE intern to present project demo and keynotes to four project leaders at Xi'an base.}
        \resumeItemListEnd
      

    \resumeSubheading
    {ShardingSphere - Open Source Promotion Plan}{Remote}
    {Student Developer}{July 2022 - Oct 2022}
        \resumeItemListStart
        \resumeItem{Development}
        {Designed a test engine to dynamic load over 100,000 SQL cases from MySQL \& PostgreSQL for SQL parser parameterized test within 1 minute, and integrated the test at remote, manually at local as well.}
        \resumeItem{Optimization}
        {Migrated test-coverage reports from Travis to GitHub Action and reduced CI cost time by at least 3-5 minutes.}
        \resumeItemListEnd
    
      
    \resumeSubheading
    {Vehicle Re-identification Defence System}{Changsha}
    {Research Assistant at the Systems Security Lab, CSU}{Nov 2020 - Nov 2021}
        \resumeItemListStart
        \resumeItem{Tasks}
        {Participated in building the feature extraction \& related testing of vehicle re-identification defence system based on Transformer, and independently designed the island of GLOM by Python.}
        \resumeItem{Researched}
        {Reported 2 papers at the group per 2 weeks, and self-researched on the interpretability of neural network.}
        \resumeItemListEnd
      
      
\resumeSubHeadingListEnd
  
  
%-----------Publication & Patents-----------------
\section{Publication \& Patents}
\vspace{4pt}

    \resumeItemSingle{\textbf{J., Yu}, Q., Zhao, W. and Zhuang et al., ``Decision and Evaluation of Ordering and Transshipment Schemes Based on Multi-objective Programming," 2021 5th Annual International Conference on Data Science and Business Analytics (ICDSBA), 2021, pp. 474-478, doi: 10.1109/ICDSBA53075.2021.00097.}
    
    
    \resumeItemSingle{\textbf{Junfeng Yu} et al., ``The Research of RoboCup2D Player Shooting Technique Based on Fuzzy Control," International Conference on Robotics Automation and Intelligent Control (ICRAIC 2021), 2022 J. Phys.: Conf. Ser. 2203 012059.}
    
    
    \resumeItemSingle{\textbf{Junfeng Yu}, (2022). \textit{Darker Corners of Go (Chinese Version)}. Beijing: Turing (Under Review)}


%-----------Projects-----------------
\section{Projects}
\resumeSubHeadingListStart 
   
    \resumeSubheadingCompact{MIT 6.824}{Oct 2022 - Nov 2022}
    {Solo Developer}
        \resumeItemListStart
        \resumeItemSingle{---------------------------------------------------------------------------------}
        \resumeItemSingle{---------------------------------------------------------------------------------}
        \resumeItemListEnd


    \resumeSubheadingCompact{Netpoll - CloudWeGo}{July 2022 - Sept 2022}
    {Awesome Contributor (Nomination)}
        \resumeItemListStart
        \resumeItemSingle{Formalized a pure Golang SDK version (without CGO) of the high-performance io\_uring I/O poller.}
        \resumeItemSingle{Approximately 3 times improvement compared to epoll, implemented default POLL for poller using io\_uring.}
        \resumeItemListEnd


    \resumeSubheadingCompact{RoboCup China Open 2D Soccer Simulation}{May 2021 - Spet 2021}
    {Varsity Captain of the Team Yunlu, CSU}
        \resumeItemListStart
        \resumeItemSingle{Accelerated the control mechanism and strategy to increase shot hit rate by 21.36\% with certain robustness.}
        \resumeItemSingle{Won 2nd price on RoboCup China Open 2D Soccer Simulation and published one paper as the first author in ICRAIC 2021.}
        \resumeItemListEnd
        
 
  \resumeSubHeadingListEnd
 
 
%--------CONFERENCES & SERVICES------------
\section{Activities \& Awards}

    \resumeItem{Awards}{2 National Awards(2nd Prize of RoboCup China Open 2D Soccer Simulation, and Outstanding Completion of 2021 CASTIC), 3 Provincial Awards(2nd Prize of the 14th Challenge Cup for College Student, 2nd Prize of the 7th Internet+ CCB Cup for College Student, and Grand Prize of the 15th Shenghua Cup for College Student), several Shool-Level Awards, etc.}
    
    
    \resumeItem{Organizations}{The president of the school-funded Apple Lab for Apple Tech Talk; The captain of the school-funded team Yunlu for RoboCup; The grade president of the Computer Science Department for department-level activities.}
    
    
%-----------STATS-----------------
\section{Skills}

  	\resumeItem{Programming Language}
    {Golang(40k LOC), Java(20k LOC), C/C++(20k LOC), JavaScript, Python, ANTLR4}
    
    
    \resumeItem{Familiar Framework \& Skillset}
    {Database Kernel Dev (C/Java/ANTLR4), Infrastructure Dev (Golang), Web Dev (Java/Golang)}


%-------------------------------------------
\end{document}
